Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-16 bdcloud_paper/latex/paper.tex
small edits.  add references

Store records contain a unique identifier and a location in the form of a 5-digit zip code.  The locations of the stores are modeled by a PMF that gives the probability that a store's location is the given zip code. We've written the PMF to give to zip codes in high-population, high-income areas the highest probabilities. The PMF is composed of two individual PMFs. One PMF determines the probability of each zip code as the population of that zip code over the total population:

@@

The second PMF scales the probabilities of the zip codes by their incomes.  The zip code with the highest-income has a probability s-times larger than that of the lowest-income zip code. The values in-between are interpolated using an exponential function:

@@

The combined PMF is given as:

@@

The PMFs are parameterized using external data sets.  The list of zip codes came from a database of zip code latitude and longitudes.  The population and household income data [reference] for the zip codes were taken from from the U.S. Census.

The stores' locations are generated by sampling zip codes from the PMF.  A variety of methods can be used such as Roulette Wheel sampling and Monte Carlo methods.

>>>>

Store records contain a unique identifier and a location in the form of a 5-digit zip code.  The locations of the stores are modeled by a PDF that gives the probability that a store's location is the given zip code. We designed the PDF to give to zip codes in high-population, high-income areas the highest probabilities. The PDF is composed of two individual PMFs. One PMF determines the probability of each zip code as the population of that zip code over the total population:

@@

The second PDF scales the probabilities of the zip codes by their incomes.  The zip code with the highest-income has a probability $s$-times larger than that of the lowest-income zip code. The values in-between are interpolated using an exponential function:

@@

The combined PDF is given as:

@@

The PDFs are parameterized using external data sets.  The zip codes' latitudes and longitudes came from the Zip Code Database Project \cite{Zips}.  The population and household income data for the zip codes were taken from from the U.S. Census American Community Survey \cite{ACS}.

The stores' locations are generated by sampling zip codes from the PDF.  A variety of methods can be used such as Roulette Wheel sampling and Monte Carlo methods.
